{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Analysis, Convergence, and Applications }

### 2024-12-17 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\subsection{The method of Inexact Momentum}

>>>>

\subsection{The method of Inexact Momentum}
    This section introduces an algorithm of our creation through the remark of Proposition \ref*{prop:stepwise-lyapunov}. 
    The algorithm estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$.

### 2024-12-17 Notebook LaTEX/Proposal/main.tex
>w<, changes

\begin{abstract} 
    \noindent
    The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
    The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
    We summarize our ongoing research in unifying Nesterov-type accelerated proximal gradient method and proposes our method of spectral momentum. 
    We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
    We present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegegation covers.

>>>>

\begin{abstract} 
    \noindent
    The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
    The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our method of spectral momentum. 
    We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
    We present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegetation covers.
